Stabilization-Free Virtual Element Methods

### 2022-06-16 stabfreevem_sinum.tex
add sinum version

\documentclass[10pt]{amsart}
%\input{/Dropbox/Math/TexDocument/mysetting.tex}
%\input{mysetting.tex}

\usepackage{amssymb}
\usepackage[leqno]{amsmath}
\usepackage{mathrsfs}
\usepackage{stmaryrd}
\usepackage{chemarrow}
\usepackage[norelsize]{algorithm2e}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage[pdftex,bookmarksnumbered,bookmarksopen,colorlinks,linkcolor=blue,anchorcolor=black,citecolor=blue,urlcolor=blue]{hyperref}
%\usepackage[dvips,bookmarksnumbered,bookmarksopen,colorlinks,linkcolor=red,anchorcolor=black,citecolor=blue,urlcolor=blue]{hyperref}
\usepackage[all]{xy}
\usepackage{tikz}
\usetikzlibrary{arrows}

\usepackage{multirow}
\usepackage[hyperpageref]{backref}

% comments
%\newcommand{\LC}[1]{\textcolor{cyan}{#1}}
\newcommand{\LC}[1]{\textcolor{red}{#1}}
\newcommand{\XH}[1]{\textcolor{red}{#1}}
%\usepackage[pdftex,colorlinks=true,citecolor=myBlue,linkcolor=myBlue]{hyperref}

  \newcounter{mnote}
  \setcounter{mnote}{0}
  \newcommand{\mnote}[1]{\addtocounter{mnote}{1}
    \ensuremath{{}^{\bullet\arabic{mnote}}}
    \marginpar{\footnotesize\em\color{red}\ensuremath{\bullet\arabic{mnote}}#1}}
  \let\oldmarginpar\marginpar
    \renewcommand\marginpar[1]{\-\oldmarginpar[\raggedleft\footnotesize #1]%
    {\raggedright\footnotesize #1}}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}
\newtheorem{exercise}[theorem]{Exercise}
\newtheorem{question}[theorem]{Question}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{alg}[theorem]{Algorithm}

\newcommand{\dx}{\,{\rm d}x}
\newcommand{\dd}{\,{\rm d}}
\newcommand{\bs}{\boldsymbol}
\newcommand{\mcal}{\mathcal}

\DeclareMathOperator*{\img}{img}
%\DeclareMathOperator*{\span}{span}
\newcommand{\curl}{\operatorname{curl}}
\renewcommand{\div}{\operatorname{div}}
%\renewcommand{\grad}{\operatorname{grad}}
\newcommand{\grad}{\operatorname{grad}}
\DeclareMathOperator*{\tr}{tr}
\DeclareMathOperator*{\rot}{rot}
\DeclareMathOperator*{\var}{Var}
\newcommand{\dev}{\operatorname{dev}}
\newcommand{\sym}{\operatorname{sym}}
\newcommand{\skw}{\operatorname{skw}}
\newcommand{\spn}{\operatorname{spn}}
\numberwithin{equation}{section}

\begin{document}
\title[Stabilization-Free VEM]{Stabilization-Free Virtual Element Methods}
\author{Chunyu Chen}%
\address{Hunan Key Laboratory for Computation and Simulation in Science and Engineering; School of Mathematics and Computational Science, Xiangtan University, Xiangtan 411105, P.R.China }%
 \email{202131510114@smail.xtu.edu.cn}%
 \author{Xuehai Huang}%
 \address{School of Mathematics, Shanghai University of Finance and Economics, Shanghai 200433, China}%
 \email{huang.xuehai@sufe.edu.cn}%
\author{Huayi Wei}%
\address{Hunan Key Laboratory for Computation and Simulation in Science and Engineering; School of Mathematics and Computational Science, Xiangtan University, Xiangtan 411105, P.R.China }%
 \email{weihuayi@xtu.edu.cn}%

 \thanks{The second author is the corresponding author. The second author was supported by the National Natural Science Foundation of China Project 12171300, and the Natural Science Foundation of Shanghai 21ZR1480500.}
 \thanks{The first and third authors were supported by NSFC (11871413) and in part by projects
of Education Department of Hunan Provincial of China (19B534, 19A500).}

\makeatletter
\@namedef{subjclassname@2020}{\textup{2020} Mathematics Subject Classification}
\makeatother
\subjclass[2020]{
%65F10;   %% Iterative numerical methods for linear systems
% 58J10;   %%  Differential complexes [See also 35Nxx]; elliptic complexes
65N12;   %%  Stability and convergence of numerical methods for boundary value problems involving PDEs;
% 65N15;   %%  Error bounds for boundary value problems involving PDEs
65N22;   %%  Numerical solution of discretized equations for boundary value problems involving PDEs;
65N30;   %%  Finite element, Rayleigh-Ritz and Galerkin methods for boundary value problems involving PDEs;
%65N55;   %%  Multigrid methods; domain decomposition for boundary value problems involving PDEs;
% 15A69;   %%  Multilinear algebra, tensor calculus
% 15A72;   %%  Vector and tensor algebra, theory of invariants [See also 13A50, 14L24]
}

\begin{abstract}
Stabilization-free virtual element methods in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming virtual element method in arbitrary dimension and a conforming virtual element method in two dimensions.
The key is to construct local $H(\div)$-conforming macro finite element spaces such that the associated $L^2$ projection of the gradient of virtual element functions is computable, and the $L^2$ projector has a uniform lower bound on the gradient of virtual element function spaces in $L^2$ norm.
Optimal error estimates are derived for these stabilization-free virtual element methods.
Numerical results are provided to verify the convergence rates.
\end{abstract}

\keywords{Virtual element, stabilization-Free, macro finite element, norm equivalence, error analysis}

@@

% \tableofcontents

@@

The key to construct stabilization-free virtual element methods is to find a finite-dimensional space $\mathbb{V}(K)$ and a projector $Q_K$ onto space $\mathbb{V}(K)$ such that
\begin{enumerate}[(C1)]
\item It holds the norm equivalence 
\begin{equation}\label{intro:gradVknormequiv} 
\|Q_{K}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K)
\end{equation}
on shape function space $V_k(K)$ of virtual elements;
\item The projection $Q_{K}\nabla v$ is computable based on the degrees of freedom (DoFs) of virtual elements for $v\in V_k(K)$.
\end{enumerate}
We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the inner product $(\cdot, \cdot)_K$. The norm equivalence \eqref{intro:gradVknormequiv} implies space $\mathbb{V}(K)$ should be sufficiently large compared with the virtual element space $V_k(K)$.
In standard virtual element methods, $Q_{k-1}^{K}\nabla v$ \cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$ \cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016} are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the $(k-1)$th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and $\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$th order polynomial space $\mathbb P_{k}(K)$.
While only
$$
\|Q_{k-1}^{K}\nabla v\|_{0,K}\lesssim \|\nabla v\|_{0,K}, \quad \|\nabla\Pi_k^{K}v\|_{0,K}\lesssim \|\nabla v\|_{0,K}
$$
hold
rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually necessary to ensure the coercivity of the discrete bilinear form.
To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
Instead, we employ $k$th order or $(k-1)$th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as usual ones.

@@

Let $\{\mathcal {T}_h\}$ denote a family of partitions
of $\Omega$ into nonoverlapping simple polytopes with $h:=\max\limits_{K\in \mathcal {T}_h}h_K$
and $h_K:=\mbox{diam}(K)$.
Denote by $\mathcal F_h^r$ the set of all $(d-r)$-dimensional faces of the partition $\mathcal T_h$ for $r=1,\ldots,d$. Set $\mathcal F_h:=\mathcal F_h^1$ for simplicity. Let $\mathcal F_h^{\partial}$ be the subset of $\mathcal F_h$ including all $(d-1)$-dimensional faces on $\partial\Omega$. 
For any $F\in\mathcal{F}_h$,
let $h_F$ be its diameter and fix a unit normal vector $\boldsymbol{n}_F$.
For a piecewise smooth function $v$, define 
$$
\|v\|_{1,h}^2:=\sum_{K\in\mathcal T_h}\|v\|_{1,K}^2,\quad |v|_{1,h}^2:=\sum_{K\in\mathcal T_h}|v|_{1,K}^2.
$$

For domain $K$, we use $\boldsymbol{H}(\div, K)$ and $\boldsymbol{H}_0(\div, K)$ to denote the standard divergence vector spaces. 
For smooth vector function $\boldsymbol{v}$, let $\nabla\boldsymbol{v}:=(\partial_iv_j)_{1\leq i,j\leq d}$.
On face $F\in\mathcal F_h$, define surface divergence
$$
\div_F\boldsymbol{v}=\div(\boldsymbol{v}-(\boldsymbol{v}\cdot\boldsymbol{n})\boldsymbol{n})=\div\boldsymbol{v}-\partial_n(\boldsymbol{v}\cdot\boldsymbol{n}).
$$
For smooth function $v$, define surface gradient $\nabla_Fv:=\nabla v-(\partial_nv)\boldsymbol{n}$.

@@

For polytope $K\in \mathcal T_h$, denote by $\mathcal T_K$ the simplicial partition of $K$, which is induced from $\mathcal T_h^*$. Let $\mathcal{F}(\mathcal T_K)$ and $\mathcal{E}(\mathcal T_K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of the simplicial partition $\mathcal T_K$ respectively. Set 
$$
\mathcal{F}^{\partial}(\mathcal T_K):=\{F\in\mathcal{F}(\mathcal T_K): F\subset\partial K\},\quad \mathcal{E}^{\partial}(\mathcal T_K):=\{e\in\mathcal{E}(\mathcal T_K): e\subset\partial K\}.
$$

@@

In this section we will construct $H(\div)$-conforming macro finite elements in arbitrary dimension.
\subsection{$H(\div)$-conforming finite elements}
For $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
$$
\boldsymbol{V}_{k-1}^{BDM}(K):=\{\boldsymbol{\phi}\in\bs H(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
$$ 
be the local Brezzi-Douglas-Marini (BDM) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}, whose degrees of freedom (DoFs) are given by \cite{ChenHuang2021divdiv}
\begin{align}
(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F, & \quad q\in \mathbb P_{k-1}(F), F\in\mathcal F(T), \label{BDMdof1} \\
(\div\boldsymbol{v}, q)_T, & \quad q\in \mathbb P_{k-2}(T)/\mathbb R, \label{BDMdof2} \\
(\boldsymbol{v}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x}. \label{BDMdof3}
\end{align}
Define $\mathring{\boldsymbol{V}}_{k-1}^{BDM}(K):=\boldsymbol{V}_{k-1}^{BDM}(K)\cap \boldsymbol{H}_0(\div, K)$.

We also need the lowest order Raviart-Thomas (RT) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}
$$
\boldsymbol{V}^{RT}(K):=\{\boldsymbol{\phi}\in\bs H(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{0}(T;\mathbb R^d)+\boldsymbol{x}\mathbb P_{0}(T) \textrm{ for each } T\in\mathcal T_K\}.
$$
Define $\mathring{\boldsymbol{V}}^{RT}(K):=\boldsymbol{V}^{RT}(K)\cap \boldsymbol{H}_0(\div, K)$.

@@

\begin{lemma}
It holds the decomposition
\begin{equation}\label{eq:Pkskwtensordecomp}  
\mathbb P_{k-2}(T;\mathbb K)=\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\oplus\big(\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})\big).
\end{equation}
\end{lemma}
\begin{proof}
Thanks to decomposition \eqref{eq:Pkvectordecomp}, we have 
$$
\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\skw\nabla(\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}).
$$
By Lemma~\ref{lem:skwgrad}, $\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\cap\big(\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})\big)=\{\boldsymbol{0}\}$. Then we only need to check dimensions.
Due to complex \eqref{eq:polycomplex1},
\begin{equation}\label{eq:20220324-1}  
\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-1}(T;\mathbb R^d)-\dim\nabla\mathbb P_k(T).
\end{equation}
On the other side, by space decomposition \eqref{eq:Pkvectordecomp},
$$
\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}=\dim\mathbb P_{k-1}(T;\mathbb R^{d})-\dim\nabla\mathbb P_k(T).
$$
Hence $\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$, which yields \eqref{eq:Pkskwtensordecomp}.
\end{proof}

@@

With the decomposition \eqref{eq:Pkskwtensordecomp} and $\mathbb P_{k-1}(F;\mathbb R^{d-1})=\nabla_FP_k(F)\oplus\mathbb P_{k-2}(F;\mathbb K)\boldsymbol{x}$, we are ready to define the finite element for differential $(d-2)$-form. Take $\mathbb P_k(T;\mathbb K)$ as the space of shape functions. The degrees of freedom are given by
\begin{align}
((\boldsymbol{n}_1^e)^{\intercal}\boldsymbol{\tau}\boldsymbol{n}_2^e, q)_e, & \quad q\in \mathbb P_k(e), e\in\mathcal E(T), \label{eq:-2formfemdof1} \\
(\div_F(\boldsymbol{\tau}\boldsymbol{n}), q)_F, & \quad q\in \mathbb P_{k-1}(F)/\mathbb R, F\in\mathcal F(T), \label{eq:-2formfemdof21} \\
(\boldsymbol{\tau}\boldsymbol{n}, \boldsymbol{q})_F, & \quad \boldsymbol{q}\in \mathbb P_{k-2}(F;\mathbb K)\boldsymbol{x}, F\in\mathcal F(T), \label{eq:-2formfemdof22} \\
(\div\boldsymbol{\tau}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in\mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x}, \label{eq:-2formfemdof31} \\
(\boldsymbol{\tau}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x}). \label{eq:-2formfemdof32}
\end{align}
In DoF \eqref{eq:-2formfemdof1}, $\boldsymbol{n}_1^e$ and  $\boldsymbol{n}_2^e$ are two unit normal vectors of $e$ satisfying $\boldsymbol{n}_1^e\cdot\boldsymbol{n}_2^e=0$. 
\begin{lemma}\label{lem:normalskwtensor}
For $e\in\mathcal E(T)$, let $\tilde{\boldsymbol{n}}_1$ and  $\tilde{\boldsymbol{n}}_2$ be another two unit normal vectors of $e$ satisfying $\tilde{\boldsymbol{n}}_1\cdot\tilde{\boldsymbol{n}}_2=0$. Then
$$
\skw(\tilde{\boldsymbol{n}}_1\tilde{\boldsymbol{n}}_2^{\intercal})=\pm\skw(\boldsymbol{n}_1^e(\boldsymbol{n}_2^e)^{\intercal}).
$$
\end{lemma}
\begin{proof}
Notice that there exists an orthonormal matrix $H\in\mathbb R^{2\times2}$ such that 
$(\tilde{\boldsymbol{n}}_1, \tilde{\boldsymbol{n}}_2)=(\boldsymbol{n}_1^e, \boldsymbol{n}_2^e)H$.
Then
\begin{align*}
2\skw(\tilde{\boldsymbol{n}}_1\tilde{\boldsymbol{n}}_2^{\intercal})&=\tilde{\boldsymbol{n}}_1\tilde{\boldsymbol{n}}_2^{\intercal}-\tilde{\boldsymbol{n}}_2\tilde{\boldsymbol{n}}_1^{\intercal}=(\tilde{\boldsymbol{n}}_1, \tilde{\boldsymbol{n}}_2)\begin{pmatrix}
0 & 1 \\
-1 & 0
\end{pmatrix}\begin{pmatrix}
\tilde{\boldsymbol{n}}_1^{\intercal} \\
\tilde{\boldsymbol{n}}_2^{\intercal}  
\end{pmatrix}
\\
&=(\boldsymbol{n}_1^e, \boldsymbol{n}_2^e)H\begin{pmatrix}
0 & 1 \\
-1 & 0
\end{pmatrix}H^{\intercal}(\boldsymbol{n}_1^e, \boldsymbol{n}_2^e)^{\intercal}.
\end{align*}
By direct computation, $H\begin{pmatrix}
0 & 1 \\
-1 & 0
\end{pmatrix}H^{\intercal}={\rm det}(H)\begin{pmatrix}
0 & 1 \\
-1 & 0
\end{pmatrix}$. Hence
$$
2\skw(\tilde{\boldsymbol{n}}_1\tilde{\boldsymbol{n}}_2^{\intercal})=2{\rm det}(H)\skw(\boldsymbol{n}_1^e(\boldsymbol{n}_2^e)^{\intercal}),
$$
which ends the proof.
\end{proof}

@@

\subsection{Discrete method}
Define the global conforming virtual element space
$$
V_h:=\{v_h\in H_0^1(\Omega): v_h|_K\in V_k(K) \textrm{ for each } K\in\mathcal T_h\}.
$$

>>>>

% SIAM Article Template
\documentclass[review,hidelinks,onefignum,onetabnum]{siamart220329}

% Information that is shared between the article and the supplement
% (title and author information, macros, packages, etc.) goes into
% ex_shared.tex. If there is no supplement, this file can be included
% directly.

\input{ex_shared}

% Optional PDF information
\ifpdf
\hypersetup{
  pdftitle={Robust Mixed Methods for Quad-Curl Perturbation Problem},
  pdfauthor={X. Huang and C. Zhang}
}
\fi

% The next statement enables references to information in the
% supplement. See the xr-hyperref package for details.

% \externaldocument[][nocite]{ex_supplement}

% FundRef data to be entered by SIAM
%<funding-group specific-use="FundRef">
%<award-group>
%<funding-source>
%<named-content content-type="funder-name"> 
%</named-content> 
%<named-content content-type="funder-identifier"> 
%</named-content>
%</funding-source>
%<award-id> </award-id>
%</award-group>
%</funding-group>

\begin{document}

@@

% REQUIRED
\begin{abstract}
Stabilization-free virtual element methods in arbitrary degree of polynomial are developed for second order elliptic problems, including a nonconforming virtual element method in arbitrary dimension and a conforming virtual element method in two dimensions. The key is to construct local $H(\div)$-conforming macro finite element spaces such that the associated $L^2$ projection of the gradient of virtual element functions is computable, and the $L^2$ projector has a uniform lower bound on the gradient of virtual element function spaces in $L^2$ norm. Optimal error estimates are derived for these stabilization-free virtual element methods. Numerical results are provided to verify the convergence rates.
\end{abstract}

% REQUIRED
\begin{keywords}
virtual element, stabilization-Free, macro finite element, norm equivalence, error analysis
\end{keywords}

% REQUIRED
\begin{MSCcodes}
65N12, 65N22, 65N30
\end{MSCcodes}

@@

The key to construct stabilization-free virtual element methods is to find a finite-dimensional space $\mathbb{V}(K)$ and a projector $Q_K$ onto space $\mathbb{V}(K)$ such that
\begin{enumerate}[(C1)]
\item It holds the norm equivalence 
\begin{equation}\label{intro:gradVknormequiv} 
\|Q_{K}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K)
\end{equation}
on shape function space $V_k(K)$ of virtual elements;
\item The projection $Q_{K}\nabla v$ is computable based on the degrees of freedom (DoFs) of virtual elements for $v\in V_k(K)$.
\end{enumerate}
We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the inner product $(\cdot, \cdot)_K$. The norm equivalence \eqref{intro:gradVknormequiv} implies space $\mathbb{V}(K)$ should be sufficiently large compared with the virtual element space $V_k(K)$.
In standard virtual element methods, $Q_{k-1}^{K}\nabla v$ \cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$ \cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016} are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the $(k-1)$th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and $\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$th order polynomial space $\mathbb P_{k}(K)$.
While only
\[
\|Q_{k-1}^{K}\nabla v\|_{0,K}\lesssim \|\nabla v\|_{0,K}, \quad \|\nabla\Pi_k^{K}v\|_{0,K}\lesssim \|\nabla v\|_{0,K}
\]
hold
rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually necessary to ensure the coercivity of the discrete bilinear form.
To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
Instead, we employ $k$th order or $(k-1)$th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as usual ones.

@@

Let $\{\mathcal {T}_h\}$ denote a family of partitions
of $\Omega$ into nonoverlapping simple polytopes with $h:=\max\limits_{K\in \mathcal {T}_h}h_K$
and $h_K:=\mbox{diam}(K)$.
Denote by $\mathcal F_h^r$ the set of all $(d-r)$-dimensional faces of the partition $\mathcal T_h$ for $r=1,\ldots,d$. Set $\mathcal F_h:=\mathcal F_h^1$ for simplicity. Let $\mathcal F_h^{\partial}$ be the subset of $\mathcal F_h$ including all $(d-1)$-dimensional faces on $\partial\Omega$. 
For any $F\in\mathcal{F}_h$,
let $h_F$ be its diameter and fix a unit normal vector $\boldsymbol{n}_F$.
For a piecewise smooth function $v$, define 
\[
\|v\|_{1,h}^2:=\sum_{K\in\mathcal T_h}\|v\|_{1,K}^2,\quad |v|_{1,h}^2:=\sum_{K\in\mathcal T_h}|v|_{1,K}^2.
\]

For domain $K$, we use $\boldsymbol{H}(\div, K)$ and $\boldsymbol{H}_0(\div, K)$ to denote the standard divergence vector spaces. 
For smooth vector function $\boldsymbol{v}$, let $\nabla\boldsymbol{v}:=(\partial_iv_j)_{1\leq i,j\leq d}$.
On face $F\in\mathcal F_h$, define surface divergence
\[
\div_F\boldsymbol{v}=\div(\boldsymbol{v}-(\boldsymbol{v}\cdot\boldsymbol{n})\boldsymbol{n})=\div\boldsymbol{v}-\partial_n(\boldsymbol{v}\cdot\boldsymbol{n}).
\]
For smooth function $v$, define surface gradient $\nabla_Fv:=\nabla v-(\partial_nv)\boldsymbol{n}$.

@@

For polytope $K\in \mathcal T_h$, denote by $\mathcal T_K$ the simplicial partition of $K$, which is induced from $\mathcal T_h^*$. Let $\mathcal{F}(\mathcal T_K)$ and $\mathcal{E}(\mathcal T_K)$ be the set of all $(d-1)$-dimensional faces and $(d-2)$-dimensional faces of the simplicial partition $\mathcal T_K$ respectively. Set 
\[
\mathcal{F}^{\partial}(\mathcal T_K):=\{F\in\mathcal{F}(\mathcal T_K): F\subset\partial K\},\quad \mathcal{E}^{\partial}(\mathcal T_K):=\{e\in\mathcal{E}(\mathcal T_K): e\subset\partial K\}.
\]

@@

In this section we will construct $H(\div)$-conforming macro finite elements in arbitrary dimension.
\subsection{$H(\div)$-conforming finite elements}
For $d$-dimensional polytope $K\in \mathcal T_h$ and $k\geq2$, let 
\[
\boldsymbol{V}_{k-1}^{BDM}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{k-1}(T;\mathbb R^d) \textrm{ for each } T\in\mathcal T_K\}
\] 
be the local Brezzi-Douglas-Marini (BDM) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}, whose degrees of freedom (DoFs) are given by \cite{ChenHuang2021divdiv}
\begin{align}
(\boldsymbol{v}\cdot\boldsymbol{n}, q)_F, & \quad q\in \mathbb P_{k-1}(F), F\in\mathcal F(T), \label{BDMdof1} \\
(\div\boldsymbol{v}, q)_T, & \quad q\in \mathbb P_{k-2}(T)/\mathbb R, \label{BDMdof2} \\
(\boldsymbol{v}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x}. \label{BDMdof3}
\end{align}
Define $\mathring{\boldsymbol{V}}_{k-1}^{BDM}(K):=\boldsymbol{V}_{k-1}^{BDM}(K)\cap \boldsymbol{H}_0(\div, K)$.

We also need the lowest order Raviart-Thomas (RT) element space~\cite{BrezziDouglasMarini1986,BrezziDouglasDuranFortin1987,Nedelec:1986family}
\[
\boldsymbol{V}^{RT}(K):=\{\boldsymbol{\phi}\in\boldsymbol{H}(\div, K): \boldsymbol{\phi}|_{T}\in \mathbb P_{0}(T;\mathbb R^d)+\boldsymbol{x}\mathbb P_{0}(T) \textrm{ for each } T\in\mathcal T_K\}.
\]
Define $\mathring{\boldsymbol{V}}^{RT}(K):=\boldsymbol{V}^{RT}(K)\cap \boldsymbol{H}_0(\div, K)$.

@@

\begin{lemma}
It holds the decomposition
\begin{equation}\label{eq:Pkskwtensordecomp}  
\mathbb P_{k-2}(T;\mathbb K)=\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\oplus\big(\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})\big).
\end{equation}
\end{lemma}
\begin{proof}
Thanks to decomposition \eqref{eq:Pkvectordecomp}, we have 
\[
\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\skw\nabla(\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}).
\]
By Lemma~\ref{lem:skwgrad}, $\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\cap\big(\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})\big)=\{\boldsymbol{0}\}$. Then we only need to check dimensions.
Due to complex \eqref{eq:polycomplex1},
\begin{equation}\label{eq:20220324-1}  
\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-1}(T;\mathbb R^d)-\dim\nabla\mathbb P_k(T).
\end{equation}
On the other side, by space decomposition \eqref{eq:Pkvectordecomp},
\[
\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}=\dim\mathbb P_{k-1}(T;\mathbb R^{d})-\dim\nabla\mathbb P_k(T).
\]
Hence $\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$, which yields \eqref{eq:Pkskwtensordecomp}.
\end{proof}

@@

With the decomposition \eqref{eq:Pkskwtensordecomp} and $\mathbb P_{k-1}(F;\mathbb R^{d-1})=\nabla_FP_k(F)\oplus\mathbb P_{k-2}(F;\mathbb K)\boldsymbol{x}$, we are ready to define the finite element for differential $(d-2)$-form. Take $\mathbb P_k(T;\mathbb K)$ as the space of shape functions. The degrees of freedom are given by
\begin{align}
((\boldsymbol{n}_1^e)^{\intercal}\boldsymbol{\tau}\boldsymbol{n}_2^e, q)_e, & \quad q\in \mathbb P_k(e), e\in\mathcal E(T), \label{eq:-2formfemdof1} \\
(\div_F(\boldsymbol{\tau}\boldsymbol{n}), q)_F, & \quad q\in \mathbb P_{k-1}(F)/\mathbb R, F\in\mathcal F(T), \label{eq:-2formfemdof21} \\
(\boldsymbol{\tau}\boldsymbol{n}, \boldsymbol{q})_F, & \quad \boldsymbol{q}\in \mathbb P_{k-2}(F;\mathbb K)\boldsymbol{x}, F\in\mathcal F(T), \label{eq:-2formfemdof22} \\
(\div\boldsymbol{\tau}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in\mathbb P_{k-3}(T;\mathbb K)\boldsymbol{x}, \label{eq:-2formfemdof31} \\
(\boldsymbol{\tau}, \boldsymbol{q})_T, & \quad \boldsymbol{q}\in \mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x}). \label{eq:-2formfemdof32}
\end{align}
In DoF \eqref{eq:-2formfemdof1}, $\boldsymbol{n}_1^e$ and  $\boldsymbol{n}_2^e$ are two unit normal vectors of $e$ satisfying $\boldsymbol{n}_1^e\cdot\boldsymbol{n}_2^e=0$. 
\begin{lemma}\label{lem:normalskwtensor}
For $e\in\mathcal E(T)$, let $\tilde{\boldsymbol{n}}_1$ and  $\tilde{\boldsymbol{n}}_2$ be another two unit normal vectors of $e$ satisfying $\tilde{\boldsymbol{n}}_1\cdot\tilde{\boldsymbol{n}}_2=0$. Then
\[
\skw(\tilde{\boldsymbol{n}}_1\tilde{\boldsymbol{n}}_2^{\intercal})=\pm\skw(\boldsymbol{n}_1^e(\boldsymbol{n}_2^e)^{\intercal}).
\]
\end{lemma}
\begin{proof}
Notice that there exists an orthonormal matrix $H\in\mathbb R^{2\times2}$ such that 
$(\tilde{\boldsymbol{n}}_1, \tilde{\boldsymbol{n}}_2)=(\boldsymbol{n}_1^e, \boldsymbol{n}_2^e)H$.
Then
\begin{align*}
2\skw(\tilde{\boldsymbol{n}}_1\tilde{\boldsymbol{n}}_2^{\intercal})&=\tilde{\boldsymbol{n}}_1\tilde{\boldsymbol{n}}_2^{\intercal}-\tilde{\boldsymbol{n}}_2\tilde{\boldsymbol{n}}_1^{\intercal}=(\tilde{\boldsymbol{n}}_1, \tilde{\boldsymbol{n}}_2)\begin{pmatrix}
0 & 1 \\
-1 & 0
\end{pmatrix}\begin{pmatrix}
\tilde{\boldsymbol{n}}_1^{\intercal} \\
\tilde{\boldsymbol{n}}_2^{\intercal}  
\end{pmatrix}
\\
&=(\boldsymbol{n}_1^e, \boldsymbol{n}_2^e)H\begin{pmatrix}
0 & 1 \\
-1 & 0
\end{pmatrix}H^{\intercal}(\boldsymbol{n}_1^e, \boldsymbol{n}_2^e)^{\intercal}.
\end{align*}
By direct computation, $H\begin{pmatrix}
0 & 1 \\
-1 & 0
\end{pmatrix}H^{\intercal}={\rm det}(H)\begin{pmatrix}
0 & 1 \\
-1 & 0
\end{pmatrix}$. Hence
\[
2\skw(\tilde{\boldsymbol{n}}_1\tilde{\boldsymbol{n}}_2^{\intercal})=2{\rm det}(H)\skw(\boldsymbol{n}_1^e(\boldsymbol{n}_2^e)^{\intercal}),
\]
which ends the proof.
\end{proof}

@@

\subsection{Discrete method}
Define the global conforming virtual element space
\[
V_h:=\{v_h\in H_0^1(\Omega): v_h|_K\in V_k(K) \textrm{ for each } K\in\mathcal T_h\}.
\]
